Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-08 paper/ijcai16.tex
paper: beautify non-linear problem.
paper: beautify the setmargin algorithm.
paper: add a couple of bullet points.

% Vectors
\newcommand{\vecvar}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\va}{\vecvar{a}}
\newcommand{\vb}{\vecvar{b}}
\newcommand{\vc}{\vecvar{c}}
\newcommand{\vd}{\vecvar{d}}
\newcommand{\ve}{\vecvar{e}}
\newcommand{\vf}{\vecvar{f}}
\newcommand{\vg}{\vecvar{g}}
\newcommand{\vh}{\vecvar{h}}
\newcommand{\vi}{\vecvar{i}}
\newcommand{\vj}{\vecvar{j}}
\newcommand{\vk}{\vecvar{k}}
\newcommand{\vl}{\vecvar{l}}
\newcommand{\vm}{\vecvar{m}}
\newcommand{\vn}{\vecvar{n}}
\newcommand{\vo}{\vecvar{o}}
\newcommand{\vp}{\vecvar{p}}
\newcommand{\vq}{\vecvar{q}}
\newcommand{\vr}{\vecvar{r}}
\newcommand{\vs}{\vecvar{s}}
\newcommand{\vt}{\vecvar{t}}
\newcommand{\vu}{\vecvar{u}}
\newcommand{\vv}{\vecvar{v}}
\newcommand{\vw}{\vecvar{w}}
\newcommand{\vx}{\vecvar{x}}
\newcommand{\vy}{\vecvar{y}}
\newcommand{\vz}{\vecvar{z}}
\newcommand{\valpha}{\vecvar{\alpha}}
\newcommand{\veps}{\vecvar{\varepsilon}}
\newcommand{\vphi}{\vecvar{\varphi}}
\newcommand{\vpsi}{\vecvar{\psi}}

@@

Let $k$ be set size and $n$ be the number of examples (answers).

@@

\begin{align}
    \max_{M, W, X}
        & \;\; M - \frac{\alpha}{k |\calD|} \sum_{i=1}^k \| \veps^{(i)} \|_1 - \frac{\beta}{k} \sum_{i=1}^k \| \vw^{(i)} \|_1 + \frac{\gamma}{k} \sum_{i=1}^k \langle \vw^{(i)}, \vx^{(i)} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k] \nonumber, \forall \; h \in [n]
    \\
        & \;\; \qquad \langle \vw^{(i)}, \vy^{(h)}_+ - \vy^{(h)}_- \rangle \geq M - \varepsilon^{(i)}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \nonumber
    \\
        & \;\; \qquad \langle \vw^{(i)}, \vx^{(i)} - \vx^{(j)} \rangle \geq M \label{cnst-ws-m}
    \\
        & \;\; \forall \; i \in [k] \nonumber
    \\
        & \;\; \qquad \vw^\bot \leq \vw^{(i)} \leq \vw^\top \nonumber
    \\
        & \;\; \forall \; i \in [k] \nonumber
    \\
        & \;\; \qquad \vx^i \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; h \in 1, \ldots, n, \forall \; i \in [k] \nonumber
    \\
        & \;\; \qquad \varepsilon^{(i)}_h \geq 0 \nonumber
    \\
        & \;\; M \geq 0 \nonumber
\end{align}

@@

\begin{algorithm}
\begin{algorithmic}[1]
    \Procedure{PESetMargin}{$Y, m; \calW, \calX, \valpha, T$}
        \State $\calA \gets \emptyset$
        \For{$t = 1, \ldots, T$}
            \State $\vw^*_1, \ldots, \vw^*_m, \vx^*_1, \ldots, \vx^*_m \gets \text{{\sc Solve}}(Y, \calA, m; \calW, \calX, \valpha)$
            \For{$\vx^*_i,\vx^*_j \in \{ \vx^*_1, \ldots, \vx^*_m \} \; \text{{\bf s.t.}} \; i < j$}
                \State $\calA \gets \calA \cup \text{{\sc QueryUser}}(\vx^*_i,\vx^*_j)$
            \EndFor
        \EndFor
        \State $\vw^*, \vx^* \gets \text{{\sc Solve}}(Y, \calA, 1; \calW, \calX, \valpha)$
        \State ${\bf return}\; \vw^*, \vx^*$
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

>>>>

% Vectors
\newcommand{\vecvar}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\va}{\vecvar{a}}
\newcommand{\vb}{\vecvar{b}}
\newcommand{\vc}{\vecvar{c}}
\newcommand{\vd}{\vecvar{d}}
\newcommand{\ve}{\vecvar{e}}
\newcommand{\vf}{\vecvar{f}}
\newcommand{\vg}{\vecvar{g}}
\newcommand{\vh}{\vecvar{h}}
\newcommand{\vi}{\vecvar{i}}
\newcommand{\vj}{\vecvar{j}}
\newcommand{\vk}{\vecvar{k}}
\newcommand{\vl}{\vecvar{l}}
\newcommand{\vm}{\vecvar{m}}
\newcommand{\vn}{\vecvar{n}}
\newcommand{\vo}{\vecvar{o}}
\newcommand{\vp}{\vecvar{p}}
\newcommand{\vq}{\vecvar{q}}
\newcommand{\vr}{\vecvar{r}}
\newcommand{\vs}{\vecvar{s}}
\newcommand{\vt}{\vecvar{t}}
\newcommand{\vu}{\vecvar{u}}
\newcommand{\vv}{\vecvar{v}}
\newcommand{\vw}{\vecvar{w}}
\newcommand{\vx}{\vecvar{x}}
\newcommand{\vy}{\vecvar{y}}
\newcommand{\vz}{\vecvar{z}}
\newcommand{\valpha}{\vecvar{\alpha}}
\newcommand{\veps}{\vecvar{\varepsilon}}
\newcommand{\vphi}{\vecvar{\varphi}}
\newcommand{\vpsi}{\vecvar{\psi}}
\newcommand{\vtheta}{\vecvar{\theta}}

@@

Let $k$ be the set size and $n$ be the number of examples (answers).

@@

\begin{align}
    \max_{M, W, X}
        & \;\; M - \frac{\alpha}{k n} \sum_{i=1}^k \| \veps^{(i)} \|_1 - \frac{\beta}{k} \sum_{i=1}^k \| \vw^{(i)} \|_1 + \frac{\gamma}{k} \sum_{i=1}^k \langle \vw^{(i)}, \vx^{(i)} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{(i)}, \vy^{(h)}_+ - \vy^{(h)}_- \rangle \geq M - \varepsilon^{(i)}_h
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \langle \vw^{(i)}, \vx^{(i)} - \vx^{(j)} \rangle \geq M \label{cnst-ws-m}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \leq \vw^{(i)} \leq \vw^\top
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{(i)} \in \calX_{\text{feasible}}
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{(i)}_h \geq 0
    \\
        & \;\; M \geq 0
\end{align}

@@

\paragraph{Set-wise Preference Elicitation.}

\begin{algorithm}
{\footnotesize
\begin{algorithmic}[1]
    \Procedure{SetMargin}{$k, \vtheta, T$}
        \State $\calQ \gets \emptyset$
        \For{$t = 1, \ldots, T$}
            \State $\vw^{(1)}, \ldots, \vw^{(k)}, \vx^{(1)}, \ldots, \vx^{(k)} \gets \text{{\sc Solve}}(\calQ, k, \vtheta)$
            \For{$\vx^{(i)},\vx^{(j)} \in \{ \vx^{(1)}, \ldots, \vx^{(k)} \} \; \text{{\bf s.t.}} \; i < j$}
                \State $\calQ \gets \calQ \cup \text{{\sc QueryUser}}(\vx^{(i)},\vx^{(j)})$
            \EndFor
        \EndFor
        \State $\vw^*, \vx^* \gets \text{{\sc Solve}}(\calQ, 1, \vtheta)$
        \State ${\bf return}\; \vw^*, \vx^*$
    \EndProcedure
\end{algorithmic}
}
\caption{The {\sc SetMargin} algorithm. Here $k$ is the set size, $\vtheta$ are
the $\alpha,\beta,\gamma$ hyperparameters, and $T$ is the maximum number of
iterations.}
\end{algorithm}

@@

\paragraph{Synthetic Dataset.} Compare against Guo's and Paolo's algorithms
in terms of both convergence rate and running time. Do not forget the
sparse variants.

\paragraph{Constructive Dataset.} The PC dataset, with and without cost
variables.
